Interpretable Neural Networks using EAGGA

### 2025-03-14 paper/main.tex
add interaction equations

>>>>

      * given layer input $\boldsymbol{x}$ and omitting bias
      * $\text{ReLU}(\boldsymbol{x})=\max(0,\sum_{j=1}^p w_p x_p)$
      * interaction not of the form $x_j \cdot x_{j'}$ as used to from LMs but of a form where the sum $w_j x_j+w_{j'} x_{j'}$ decides whether $x_j,x_{j'}$
        pass through the activation or not
      * in other words: $\max(0,w_j x_j + w_{j'} x_{j'})\neq\max(0,w_j x_j)+\max(w_{j'} x_{j'})$ and thus there is an interaction
